..................E-commerce User Platform Requirements Analysis.....................

(1) Brand .............................
    1. User should browser Product according to Brand
    2. Each Brand should have a name, logo, description
    3. Brand should be displayed product to help users identify products from specific manufacturers

(2) Categories...........................................
    1. The stystem needs a Category structure to organize product
    2. Categories should be easy to menage.
    3. User should browser product according to Category

(3) products .................................................
    1. Product should have attributes such as name, description, price, stock status.
    2. User should be able to search, filter, sort, product based on various criteria.
    3. Easy section for "Popular", "New" ,"Top", "Special" "Regular'
    4. Must have slider section to featured product 
    5. Product should have it details & Reviews
    6. Similar product should listed below the one product details

(4) Product details ...............................
    1. Details product pages should include comprehensive information, Image, Reviews.
    2. User should be able to see product availability related product

(5) Product Reviews ........................................
    1. User should be able to leave Reviews, Rating for product.
    2. Reviews should display user Name, Rating, comments.

(6) Product Sliders..............................................
    1. The platform should support dynamic slider to shwocase featured products.
    2. Administrators should be able to select product to be display in the slider.
    3. Sliders should be customizable in terms of layout and appearce.

(7) Customers Profiles ........................................
    1. User should be able to create manage their profile.
    2. Profiles should include personal information, order, history, saved address.
    3. The platform should have easy 2 step OTP based login stystem.

(8) Product Carts...............................
    1. User should be able to add, remove product from their shopping carts.
    2. Cart should display product details, quantity, prices, total amount.
    3. User should have the option to save carts for later or proced to checkout.

(9) Porduct Wishs............................................................
    1. user should be able to create, manage WishList of products.
    2. WishList should be linked to user profile for easy access
    3. User should have the option to move items from their WishList to their cart.

(10) invoice.............................................................
     1. Each Successful transation should generate an invoice.
     2. invoice should contain details such as order number, date, total amount, billing information.
     3. User should be able to view, download their invoice from their accounts.

(11) invoice Product.......................................................
     1. Each invoice should list the products purchased in that transation.
     2. the list should include product Name, quantity, price, subtotal for eatch items.
     3. Totals should include subtotal, vat, other cahnrges.

(12) SSL commerce payment getway...........................................
     1. The platform needs integration with SSL commererce for secure payment.
     2. User should be able to link their SSL Commerce for seamless transation.
     3. Payment processing should be encrypted, compliant with security standards.